%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,letterpaper, sans]{article}     
%\usepackage[letterpaper, left=0.7in, right=0.7in,top=0.5in, bottom=0.5in]{geometry} 
\usepackage[top=0.5in, bottom=0.5in, left=0.8in, right=0.8in]{geometry}  
\usepackage{xcolor}

\usepackage{xeCJK}
\setCJKsansfont{Heiti SC}
\setCJKmainfont[BoldFont=Heiti SC Medium]{Heiti SC Light}
\renewcommand\familydefault{\sfdefault} 

\usepackage[T1]{fontenc}
\usepackage[none]{hyphenat}
\pagenumbering{gobble}

\usepackage{enumitem}
\usepackage{tabularx}
\usepackage[leftmargin=0.2in, itemsep=0in]{etaremune}

%\graphicspath{{../}}
%\setlength\parindent{0pt}

%\setlength{\hintscolumnwidth}{5cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% highlight \name in Publications
\newcommand{\tname}[1]{{\bf #1}}%{\underline{#1}}


% new section title
\newcommand{\newsec}[1]{\subsection*{\hspace{-1.5pt}\Large\uppercase{\bf #1}}}

% personal data
\def\name{林義軒, PhD}

\def\header{
\begin{center}
{\LARGE\bf \name} \vspace{0.3cm} \\
yi-hsuan.lin@outlook.com
| $+$1-416-829-6531 | 
\href{https://www.linkedin.com/in/yihsuanlinphysics/}{www.linkedin.com/in/yihsuanlinphysics}
%\href{http://individual.utoronto.ca/yihsuanlin}{individual.utoronto.ca/yihsuanlin} \\
%\href{https://laphysique.github.io}{laphysique.github.io}
\end{center}

}


\usepackage{hyperref}
\hypersetup{
    colorlinks = true,
    urlcolor = black,
    linkcolor = black,
    citecolor = black,
  pdfauthor = {\name},
  %pdfkeywords = {physics, biophysics},
  pdftitle = {\name: publication list},
  pdfsubject = {publication list},
  pdfpagemode = UseNone
}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

% Header
\header


%\begin{center}
%\section*{\Large Peer-Reviewed Publications}
%\end{center}

%\vspace{-1em}\ \

\begin{flushleft}

\newsec{發表論文}

\begin{etaremune}[leftmargin=17pt]

\item S. Das, \tname{Y.-H. Lin}, R. M. Vernon, J. D. Forman-Kay, and H. S, Chan (2020)
Comparative roles of charge, $\pi$, and hydrophobic interactions in sequence-dependent phase separation of intrinsically disordered proteins. 
{\it Proc. Natl. Acad. Sci. U.S.A.} {\bf 117}, 28795--28805

\item 
A. N. Amin$^*$, \tname{Y.-H. Lin}$^*$, S. Das, and H. S. Chan (2020)
Analytical theory for sequence-specific binary fuzzy complexes of charged intrinsically disordered proteins.
%Preprint: arXiv:1910.11194 
{\it J. Phys. Chem. B} {\bf 124}, 6709--6720 \\
($^*$equal contribution; selected supplementary cover) 

\item
\tname{Y.-H. Lin}, J. P Brady, H. S. Chan, and K. Ghosh (2020)
A unified analytical theory of heteropolymers for sequence-specific phase behaviors of polyelectrolytes and polyampholytes. 
{\it J. Chem. Phys.} {\bf 152}, 045102

\item
H. Cinar, R. Oliva, \tname{Y.-H. Lin}, X. Chen, M. Zhang, H. S. Chan, and R. H. A. Winter (2020)
Pressure sensitivity of SynGAP/PSD-95 condensates as a model for postsynaptic densities and its biophysical and neurological ramifications. 
{\it Chem. Eur. J.} {\bf 26}, 11024--11031 (cover feature)

\item
S. Das, A. N. Amin, \tname{Y.-H. Lin}, and H. S. Chan (2018)
Coarse-grained residue-based models of disordered protein condensates: utility and limitations of simple charge pattern parameters, {\it Phys. Chem. Chem. Phys.} {\bf 20}, 28558--28574

\item
\tname{Y.-H. Lin}, J. D. Forman-Kay, and H. S. Chan (2018)
Theories for sequence-dependent phase behaviors of biomolecular condensates.
{\it Biochemistry} {\bf 57}, 2499--2508

\item 
S. Das, A. Eisen, \tname{Y.-H. Lin}, and H. S. Chan (2018)
A lattice model of charge-pattern-dependent polyampholyte phase separation.
{\it J. Phys. Chem. B} {\bf 122}, 5418--5431

\item
\tname{Y.-H. Lin}, J. P. Brady, J. D. Forman-Kay, and H. S. Chan (2017) 
Charge pattern matching as a ``fuzzy'' mode of molecular recognition for the functional phase separations of intrinsically disordered proteins.
{\it New J. Phys.} {\bf 19}, 115003

\item 
J. P. Brady, P. J. Farber, A. Sekhar, \tname{Y.-H. Lin}, R. Huang, A. Bah, T. J. Nott, H. S. Chan, A. J. Baldwin, J. D. Forman-Kay, and L. E. Kay (2017) 
Structural and hydrodynamic properties of an intrinsically disordered region of a germ-cell specific protein upon phase separation. 
{\it Proc. Natl. Acad. Sci. U.S.A.} {\bf 114}, E8194--E8203

\item
\tname{Y.-H. Lin} and H. S. Chan (2017) 
Phase separation and single-chain compactness of charged disordered proteins are strongly correlated. 
{\it Biophys. J.} {\bf 112}, 2043--2046

\item 
\tname{Y.-H. Lin}, J. Song, J. D. Forman-Kay, and H. S. Chan (2017) 
Random-phase-approximation theory for sequence-
dependent, biologically functional liquid-liquid phase separation of intrinsically disordered proteins. 
{\it J. Mol. Liq.} {\bf 228}, 176--193

\item
\tname{Y.-H. Lin}, J. D. Forman-Kay, and H. S. Chan (2016) 
Sequence-specific polyampholyte phase separation in membraneless organelles. 
{\it Phys. Rev. Lett.} {\bf 117}, 178101

\item 
\tname{Y.-H. Lin} and R. Bundschuh (2015) 
RNA structure generates natural cooperativity between single-stranded RNA binding proteins targeting 5' and 3'UTRs.
{\it Nucleic Acids Res.} {\bf 43}, 1160--1169

\item 
\tname{Y.-H. Lin} and R. Bundschuh (2013) 
Interplay between single-stranded binding proteins on RNA secondary structure.
{\it Phys. Rev. E} {\bf 88}, 052707
\end{etaremune} 

%\end{flushleft}


%\begin{center}
%\vspace{6pt}

%\begin{center}
%\section*{\Large Working Papers}
%\end{center}

%\vspace{-1em}\ \

%\begin{flushleft}

{\bf\large 論文預印本}

\begin{itemize}[leftmargin=*, itemsep=0in]

\item 
J. Wessén, T. Pal,  S. Das, \tname{Y.-H. Lin}, and H. S. Chan (2021)
A simple explicit-solvent model of polyampholyte phase behaviors and its ramifications for dielectric effects in biomolecular condensates.
Preprint: arXiv: 2102.03687 

\item 
J. Gaither, \tname{Y.-H. Lin}, and R. Bundschuh (2016) 
RBPBind: quantitative prediction of protein-RNA interactions. 
Preprint: arXiv:1611.01245 %[q-bio.BM]

\end{itemize} 


\newsec{受邀演講}

\begin{etaremune}[leftmargin=17pt]

\item 加拿大曼尼托巴大學物理學系 \hfill 2020年11月25日 \\
主題：生物非均相聚合物的高分子物理場論

\item 美國生物物理學年會無序蛋白組年度學術報告 \hfill 2019年3月2日 \\
主題：帶電無序蛋白序列特異性的高分子理論與仿真模擬 \\
(年度博士後獎項特別演講)

\item 中國科學院化學研究所 \hfill 2018年10月15日 \\
主題：無序蛋白序列特異性的液--液相分離理論與仿真模擬

\item 北京大學定量生物學研究中心 \hfill 2018年10月15日 \\
主題：無序蛋白序列特異性的液--液相分離理論與仿真模擬

\item 武漢華中師範大學生物物理研究所 \hfill 2018年10月12日\\
主題：生物體內液--液相分離的理論與仿真模擬


\item 多倫多大學生物化學系學術交流會 \hfill 2018年10月2日 \\
主題：無序蛋白序列特異性的液--液相分離理論

\item 蛋白質折疊研究學社(於美國加州柏克萊大學) \hfill 2017年6月3日 \\
主題：帶電無序蛋白在液--液相分離中的序列特異性

\item 多倫多兒童醫院分子結構暨功能研究中心 \hfill 2015年3月12日 \\
主題：RNA二級結構與單鍊結合蛋白的相互作用

\item 理論生物物理中心(於美國萊斯大學) \hfill 2014年10月27日 \\
主題：RNA二級結構與單鍊結合蛋白的相互作用

\item 國立成功大學國家理論物理中心(台灣) \hfill 2014年6月9日 \\
主題：RNA二級結構與單鍊結合蛋白的相互作用


\end{etaremune} 


\end{flushleft}

\bigskip





\end{document}

%% end of file `template.tex'.
