\documentclass[11pt]{../yhlcv}     

\def\tname#1{{\bf #1}}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

\title{Publications}
\name{Yi-Hsuan Lin, PhD}
\mobile{416-829-6531}
\email{yi-hsuan.lin@outlook.com}
\linkedin{yihsuanlinphysics}
\github{laphysique}

\maketitle

\raggedright


\section*{Peer-Reviewed Publications}

\begin{etaremune}[leftmargin=0.26in]\itemsep-0.2pt

\item
\tname{Lin Y-H}, Kim TH, Das S, Pal T, Wessén J, Rangadurai AK, Kay LE, Forman-Kay JD, and Chan HS (2024)
Electrostatics of Salt-Dependent Reentrant Phase Behaviors Highlights Diverse Roles of ATP in Biomolecular Condensates.
{\it eLife} {\bf 13}:RP100284

\item
\tname{Lin Y-H}, Wessén J, Pal T, Das S, and Chan HS (2023)
Numerical techniques for applications of analytical theories to sequence-dependent phase separations of intrinsically disordered proteins.
In {\it Phase-Separated Biomolecular Condensates: Methods and Protocols} {\bf 2563} 51-94

\item
Gaither J$^*$, \tname{Lin Y-H}$^*$, and Bundschuh R (2022)
RBPBind: quantitative prediction of protein-RNA interactions.
{\it J Mol Biol} {\bf 434} 167515
($^*$equal contribution)

\item 
\tname{Lin Y-H}, Wu H, Jia B, Zhang M, and Chan HS (2022)
Assembly of model postsynaptic densities involves interactions auxiliary to stoichiometric binding.
{\it Biophys J} {\bf 121} 151--171

\item 
Wessén J, Pal T, Das S, \tname{Lin Y-H}, and Chan HS (2021)
A simple explicit-solvent model of polyampholyte phase behaviors and its ramifications for dielectric effects in biomolecular condensates.
{\it J Phys Chem B} {\bf 125} 4337--4358 %(selected supplementary cover)

\item 
Das S, \tname{Lin Y-H}, Vernon RM, Forman-Kay JD, and Chan HS (2020)
Comparative roles of charge, $\pi$, and hydrophobic interactions in sequence-dependent phase separation of intrinsically disordered proteins.
{\it Proc Natl Acad Sci USA} {\bf 117} 28795--28805

\item 
Amin AN$^*$, \tname{Lin Y-H}$^*$, Das S, and Chan HS (2020)
Analytical theory for sequence-specific binary fuzzy complexes of charged intrinsically disordered proteins.
{\it J Phys Chem B} 
{\bf 124} 6709--6720
($^*$equal contribution) %, selected supplementary cover) 

\item
\tname{Lin Y-H}, Brady JP, Chan HS, and Ghosh K (2020)
A unified analytical theory of heteropolymers for sequence-specific phase behaviors of polyelectrolytes and polyampholytes. 
{\it J Chem Phys} {\bf 152} 045102

\item
Cinar H, Oliva R, \tname{Lin Y-H}, Chen X, Zhang M, Chan HS, and Winter RHA (2020)
Pressure sensitivity of SynGAP/PSD-95 condensates as a model for postsynaptic densities and its biophysical and neurological ramifications. 
{\it Chem Eur J} {\bf 26} 11024--11031 %(cover feature) 

\item 
Das S, Amin AN, \tname{Lin Y-H}, and Chan HS (2018)
Coarse-grained residue-based models of disordered protein condensates: 
utility and limitations of simple charge pattern parameters.
{\it Phys Chem Chem Phys} {\bf 20} 28558--28574 

\item
\tname{Lin Y-H}, Forman-Kay JD, and Chan HS (2018)
Theories for sequence-dependent phase behaviors of biomolecular condensates.
{\it Biochemistry} {\bf 57} 2499--2508

\item 
Das S, Eisen A, \tname{Lin Y-H}, and Chan HS (2018)
A lattice model of charge-pattern-dependent polyampholyte phase separation.
{\it J Phys Chem B} {\bf 122} 5418--5431

\item
\tname{Lin Y-H}, Brady JP, Forman-Kay JD, and Chan HS (2017) 
Charge pattern matching as a ``fuzzy'' mode of molecular recognition for the functional phase separations of intrinsically disordered proteins.
{\it New J Phys} {\bf 19} 115003

\item 
Brady JP, Farber PJ, Sekhar A, \tname{Lin Y-H}, Huang R, Bah A, Nott TJ, Chan HS, Baldwin AJ, Forman-Kay JD, and Kay LE (2017) 
Structural and hydrodynamic properties of an intrinsically disordered region of a germ-cell specific protein upon phase separation. 
{\it Proc Natl Acad Sci USA} {\bf 114} E8194--E8203

\item
\tname{Lin Y-H} and Chan HS (2017) 
Phase separation and single-chain compactness of charged disordered proteins are strongly correlated. 
{\it Biophys J} {\bf 112} 2043--2046

\item 
\tname{Lin Y-H}, Song J,Forman-Kay JD, and Chan HS  (2017) 
Random-phase-approximation theory for sequence-dependent, biologically functional liquid-liquid phase separation of intrinsically disordered proteins. 
{\it J Mol Liq} {\bf 228} 176--193

\item
\tname{Lin Y-H}, Forman-Kay JD, and Chan HS (2016) 
Sequence-specific polyampholyte phase separation in membraneless organelles. 
{\it Phys Rev Lett} {\bf 117} 178101

\item 
\tname{Lin Y-H} and Bundschuh R (2015) 
RNA structure generates natural cooperativity between single-stranded RNA binding proteins targeting 5' and 3'UTRs.
{\it Nucleic Acids Res} {\bf 43} 1160--1169

\item 
\tname{Lin Y-H} and Bundschuh R (2013) 
Interplay between single-stranded binding proteins on RNA secondary structure.
{\it Phys Rev E} {\bf 88} 052707

\end{etaremune} 

\section*{Working Papers}

\begin{itemize}[leftmargin=*]\itemsep-0.2pt
\item
Fayet A, Ayoub A, Fejes A, Janežič M, \tname{Lin Y-H}, Moitessier A, Moitessier N, Neal M, Pottel J, Rostaing O, Weiser B, Zoldan J, and Burai-Patrascu M (2025)
The Sixth CACHE Challenge -- A Comprehensive Drug Discovery Workflow to Discover Potential Inhibitors of the Triple Tudor Domain of SETDB1.
{\it ChemRxiv}, DOI:10.26434/chemrxiv-2025-jrtx9
\end{itemize} 


\end{document}


